---
title: "Height and Weight in Women"
author: "Angela"
date: "5/18/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview of Assignmennt

After makinng a ShinyApp, it's time to make your pitch. You get 5 slides (inclusive of the title slide) to pitch a your app. You're going to create a web page using Slidify or Rstudio Presenter with an html5 slide deck. Your presentation must satisfy the following:  

-It must be done in Slidify or Rstudio Presenter  
-It must be 5 pages  
-It must be hosted on github or Rpubs  
-It must contained some embedded R code that gets run when slidifying the document  

## Import Data

Using the "women" dataset from base R. This dataset represents the average heights and weights of American women. My App allows the users to compare themselves to the average.

```{r dataset,  comment = " ", format = "markdown"}
data(women)
head(women)
```

## Using the App

1. Open the link: <https://crista904.shinyapps.io/WomenBMI/?_ga=2.48766438.1110934670.1589819382-246637652.1589819382>
2. First the user needs to input their height.  
3. Then the user needs to input their weight.  
4. This will give them a BMI calculation.
5. See the intersect between the red and blue line and compare yourself to the average (open dot) American women height and weight.
6. Aim for a healthy BMI (see next slides).
 
## BMI Calculation

For example:  

```{r BMI calc, include = TRUE, echo = TRUE}
height <- 70 #inches
weight <- 120 #pounds (lbs)
BMI <- (703 * weight / (height^2))
BMI
```

## Healthy BMI

How do you know if you are healthy or not?  
  
  
Less than 18.5 = underweight  

18.5-24.9 = ideal  

Greater than 30 = obese  
